Argennon: A Scalable Smart Contract Platform

### 2021-06-21 tex/A.tex
Update persistence section
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>
Update the rest of the document
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>
Add the pronunciation note
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>
Add the Argennon consensus protocol
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>
Refactor project file structure
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

% Preamble
\documentclass[11pt, a4paper]{report}
\usepackage[a4paper]{geometry}

% Packages
%\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{amsfonts}
\usepackage[ruled,boxed]{algorithm2e}
\usepackage{algpseudocode}
\usepackage{listings}
\usepackage{amssymb}
\usepackage{tcolorbox}
\usepackage{amsmath}

@@

    \chapter{The Argennon Blockchain}\label{ch:argennon-blockchain}
    \input{sections/blockchain}

>>>>

\documentclass[11pt, a4paper]{report}
\usepackage[a4paper]{geometry}

% Packages
\usepackage{tipa}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{amsfonts}
\usepackage[ruled,boxed]{algorithm2e}
\usepackage{algpseudocode}
\usepackage{listings}
\usepackage{amssymb}
\usepackage{tcolorbox}
\usepackage{amsmath}

@@

    \chapter{Infrastructure}\label{ch:infrastructure}

    \section{Persistence Layer}\label{sec:persistence-layer}
    \input{sections/persistence}

    \section{Networking Layer}\label{sec:networking-layer}
    Unlike conventional blockchains, Argennon does not use a p2p network architecture. Instead, it uses a
    client-server topology, based on a permission-less list of ZK-EDB servers. ZK-EDB servers are a
    crucial part of the Argennon ecosystem, and they form the backbone of the Argennon networking layer.
    \note{not yet written...}

    \subsection{Censorship Resilient Mode}\label{subsec:cens-res-mode}
    \note{not yet written...}

    \chapter{The Argennon Blockchain}\label{ch:argennon-blockchain}
    \input{sections/elements}

    \section{Blocks}\label{sec:blocks}
    \input{sections/blocks}

    \section{Consensus}\label{sec:consensus}
    \input{sections/consensus}

    \section{Incentive mechanism}\label{sec:incentive-mechanism}
    \input{sections/incentive}

    \section{Concurrency}\label{sec:concurrency}
    \input{sections/concurrency}

    \section{Governance}\label{sec:governance}
    The Argennon Decentralized Autonomous Governance system (ADAGs)
    \note{not yet written...}

### 2021-06-21 tex/sections/persistence.tex
Refactor project file structure
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

The Argennon Virtual Machine has two persistent memory areas: \emph{method area}, and \emph{heap}. Method area stores
method byte codes\footnote{also it stores constant area blocks.}, and heap stores memory chunks. Both of these
data elements, methods and chunks, can be considered as continuous pieces of byte addressable memory. Throughout this
chapter, we shall call these data elements \emph{objects}.

@@

A block proposer usually obtains clustering directives from a third party source that enjoys a considerable amount of
computational power.\footnote{we can say the AVM clustering algorithm is essentially off-chain.} This federated approach
does not affect Argennon security, because the integrity of a database can not be altered by clustering directives.
Those directives can only affect the performance of the argennon blockchain, and directives of a single block can
not change the performance much.

>>>>

The Argennon Virtual Machine has two persistent memory areas: \emph{method area}, and \emph{heap}. Method area stores
bytecodes of methods\footnote{also it stores constant area blocks.}, and heap stores memory chunks. Both of these
data elements, bytecodes and chunks, can be considered as continuous pieces of byte addressable memory. Throughout this
chapter, we shall call these data elements \emph{objects}.

\subsection{Storage Pages}\label{subsec:pages}

@@

A block proposer could obtain clustering directives from any third party source\footnote{we can say the AVM clustering
algorithm is essentially off-chain.}. This will not
affect Argennon security, since the integrity of a database can not be altered by clustering directives.
Those directives can only affect the performance of the argennon blockchain, and directives of a single block can
not affect the performance considerably.

\subsubsection[Implementation]{Implementation Based on Vector Commitments}\label{subsubsec:impl-zk-edbs}

\note{not yet written...}

\subsection{Object Clustering Algorithm}\label{subsec:clustering}

\note{not yet written...}
